Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-10-06 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:10:06	11:46:24	(Tue 6.Oct)

We show that a robust MVDR implementation typically creates responses ranging between that of the rectangular and Hamming, or Kaiser windows with $\beta\in[0,2]$, respectively. We let LCA select from a set of Kaiser windows in this range, and add some variations of steering to each window. When up to their -3dB width.

each with a little steering added.

 We find that when Steering to -3\,dB width of the window. This lead to a predictable resolution gain of . design LCA's window database with windows that resembles  constrained to work in active sonar imaging the typical window responses LCA is allowed to choose from windows that are typical solutions found by the minimum variance distortionless response (MVDR) method.

@@

% Keywords (normally not used for peer reviews)
\ifPeerReview\else
\begin{IEEEkeywords}\color{gray}
Beamforming, adaptive beamforming, MVDR, LCA, sonar, active, complexity.
\end{IEEEkeywords}
\fi}
% \fi

>>>>

We show that a robust MVDR implementation typically creates responses ranging between that of the rectangular and Hamming. We let LCA select from a set of Kaiser windows with responses in this range, and add some steered variations of each. The amount of steering is limited to roughly half the response's -3\,dB width.

Using experimental data we find that LCA and MVDR produces nearly identical images of large scenes. On point targets LCA is able to double the resolution compared to DAS, of provide half that of MVDR. This performance is achieved with a total of 6 windows; the unsteered rectangular and Kaiser window with $\beta=5$, and left and right steered versions out to the steering limit. Adding a few extra windows makes the image slightly smoother.

@@

% Keywords (normally not used for peer reviews)
\ifPeerReview\else
\begin{IEEEkeywords}
Beamforming, adaptive beamforming, MVDR, LCA, sonar, active, complexity.
\end{IEEEkeywords}
\fi}
% \fi
